
\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{banking}                     
\moderncvcolor{blue}                       

\renewcommand{\familydefault}{\sfdefault}         
\nopagenumbers{}                                 

\usepackage[utf8]{inputenc}

\usepackage[scale=0.8]{geometry}

\name{Callum}{Guthrie}
\title{Curriculum Vitae}            \address{20 Gardrum Gardens, Shieldhill}{Falkirk, FK1 2TB }{Scotland}
\phone[mobile]{+44 7860 600 623}                  
\phone[fixed]{+44~1324~712~497}                                        
\email{callumgwguthrie@gmail.com}                           

\begin{document}


\makecvtitle

\section{Academic Qualifications}
\cventry{August 2012 -- June 2016}{BSc (Hons) Computer Science}{Heriot Watt University}{Edinburgh}{Predicted 2:1}{}
\cventry{August 2004 -- June 2010}{Scottish Highers}{Braes High School}{Falkirk}{}{}{}
4 passes : English, Mathematics and Modern Studies at grade B and Physical Education at grade C
\section{Applicable Experience}
\subsection{Dissertation Thesis}
\cventry{May 2016}{Abstract}{A Comparison of NoSQL and Indexing Solutions for Big Data}{}{}{}
\begin{itemize}
\item Implement and analyse several versions of prototype applications with each version employing a different technology.
\begin{itemize}
\item Technologies used : \textit{Cassandra, Elastic Search, GraphDB, MongoDB, MySQL} and \textit{Neo4j}
\end{itemize}
\item  Compare and contrast the functionality, performance and analytical capabilities of the different solutions.
\item Using a real world dataset from the biological environment and following an Extract Transform Load methodology on multiple data sources.
\end{itemize}
\subsection{Work Experience}
\cventry{May 2015-- Present}{Client Services Data Analyst}{TVSquared}{Edinburgh}{}{}
\begin{itemize}
\item Manipulating, cleansing and processing data using \textit{Excel, MongoDB} and \textit{PostgreSQL.}
\item Responsible for loading, extracting and validation of client data.
\item Analysing raw data, drawing conclusions and developing recommendations
\item Data entry, data auditing, creating data reports and monitoring all data for accuracy.
\item Troubleshoot with clients from around the world.
\item Supplying qualitative and quantitative data to colleagues and clients.
\end{itemize}
\cventry{February 2015 -- June 2015}{Corporate Database Project Volunteer}{Children 1ST}{Edinburgh}{}{}
\begin{itemize}
\item Extensive use of the fundraising database tool \textit{Raiser's Edge (Blackbaud, Inc.)}
\item Ensure that the corporate fundraising team has all database records up to date and amend any records where changes have occurred.
\item Advising on the suitability of methodologies and suggesting improvements.
\item Work on the database project so that historical records are correct and in-line with database protocols.
\end{itemize}
\cventry{October 2011 -- July 2015}{Customer Assistant}{Marks and Spencer}{Livingston}{}{}
\begin{itemize}
\item Responsible for maintaining a database which correlates information concerning the company's energy saving strategy.
\item Retrieve information regarding the store's energy saving performance and update the database accordingly.
\end{itemize}
\newpage
\newgeometry{top=3cm, left=2cm, right=2cm}
\section{Technical Abilities}
\textbf{\\Java and Python}
\begin{itemize}
\item Experience in using advanced trees, string processing, graphs and hash tables using a variety of libraries.
\item Designed several programs in \textit{Java} such as aeroplane route planners, compilers and data dictionaries.
\item Implemented several search algorithms such as depth first search, breadth first search, uniform cost search and A* search using \textit{Python.}
\end{itemize}
\textbf{MySQL and PostgreSQL}
\begin{itemize}
\item Created and maintained several \textit{MySQL} databases including designing a database structure as a relational data model for a tour guide company.
\item Implemented and maintained the backend database using \textit{PostgreSQL} for a wealth management application for financial advisers to control their clients stocks and shares.
\end{itemize}
\textbf{HTML5, CSS3 and JavaScript }
\begin{itemize}
\item Constructed a variety of data visualisations such as choropleth maps, tree maps and waterfall charts, using \textit{D3} and the \textit{Google API.}
\item Co-founder of a web development company \textit{Techni-Cals} alongside one of my fellow computer science students. We have designed a variety of web pages including static, dynamic and e-commerce.
\end{itemize}
\section{Significant Achievements}
\textbf{\\TVSquared}
\begin{itemize}
\item Started as a summer intern in May 2015, and was then offered a permanent contract in September 2015 to work on a part time basis, coinciding with studies.
\end{itemize}
\textbf{Marks and Spencer}
\begin{itemize}
\item Voted employee of the month on four occasions for providing excellent customer service and going above and beyond the expectations of the job role.
\item Elected member of the Big Involvement Group (BIG). BIG plays a major part in ensuring everyone counts, providing good conditions for work and consulting employees about matters which affect them.
\item Appointed Plan A champion for the store. Plan A is a green strategy with emphasis on cutting waste,saving energy, trading fairly and promoting animal welfare.
\end{itemize}
\textbf{Scott Logic Best Group Prize}
\begin{itemize}
\item Awarded the prize for producing the best overall year long university software engineering project.
\item Part of a team which developed a wealth management application for financial advisers to control their clients stocks and shares.
\item Worked as the group liaison and software engineer implementing the backend database in \textit{PostgreSQL} and frontend using \textit{Ruby on Rails.}
\end{itemize}
\textbf{Silver Duke of Edinburgh Award}
\begin{itemize}
\item Effective communication was essential in order to succeed in achieving the award.
\item Completed a challenging walking expedition where, at times, I had to fulfil both a leadership and team playing role.
\end{itemize}
\section{Hobbies and Interests}
\begin{itemize}
\item Played football competitively from a young age and was captain of my team throughout my playing career.
\item Undertook a coaching role for my team in 2009. I lead team training sessions and took control of several matches.
\item  I enjoy listening to music, going to the gym to keep fit and meeting up with friends.
\end{itemize}



\end{document}
