\cvsection{Significant Achievments}
\begin{cventries}
  \cventry
    {TVSquared}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item {Started as a summer intern in May 2015, and was then offered a permanent contract in September 2015 to work on a part time basis, coinciding with studies.}
      \end{cvitems}
    }
  \cventry
    {Marks and Spencer}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item {Voted employee of the month on four occasions for providing excellent customer service and going above and beyond the expectations of the job role.}
        \item {Elected member of the Big Involvement Group (BIG). BIG plays a major part in ensuring everyone counts, providing good conditions for work and consulting employees about matters which affect them.}
        \item {Appointed Plan A champion for the store. Plan A is a green strategy with emphasis on cutting waste,saving energy, trading fairly and promoting animal welfare.}
      \end{cvitems}
    }
  \cventry
    {University}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item {Awarded the Scott Logic Best Group Prize for producing the best overall year long university software engineering project.}
        \item {Part of a team which developed a wealth management application for financial advisers to control their clients stocks and shares.}
        \item {Worked as the group liaison and software engineer implementing the backend database in PostgreSQL and frontend using Ruby on Rails.}
      \end{cvitems}
    }
  \cventry
    {Silver Duke of Edinburgh Aware}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item {Effective communication was essential in order to succeed in achieving the award.}
        \item {Completed a challenging walking expedition where, at times, I had to fulfil both a leadership and team playing role.}
      \end{cvitems}
    }
\end{cventries}
