\cvsection{Applicable Experience}
\begin{cventries}
  \cventry
    {Client Services Data Analsyt}
    {TVSquared}
    {Edinburgh, Scotland}
    {May. 2015 - PRESENT}
    {
      \begin{cvitems}
        \item {Manipulating, cleansing and processing data using \textit{Excel, MongoDB} and \textit{PostgreSQL}.}
        \item {Responsible for loading, extracting and validation of client data.}
        \item {Analysing raw data, drawing conclusions and developing recommendations}
        \item {Data entry, data auditing, creating data reports and monitoring all data for accuracy.}
        \item {Troubleshoot with clients from around the world.}
        \item {Supplying qualitative and quantitative data to colleagues and clients.}
      \end{cvitems}
    }
  \cventry
    {Corporate Database Project Volunteer}
    {Children 1ST (Charity)}
    {Edinburgh, Scotland}
    {Feb. 2015 - Jun. 2015}
    {
      \begin{cvitems}
        \item {Extensive use of the fundraising database tool \textit{Raiser's Edge (Blackbaud, Inc.)}}
        \item {Ensure that the corporate fundraising team has all database records up to date and amend any records where changes have occurred.}
        \item {Advising on the suitability of methodologies and suggesting improvements.}
        \item {Work on the database project so that historical records are correct and in-line with database protocols.}
      \end{cvitems} 
    }
  \cventry
    {Customer Assistant}
    {Marks and Spencer}
    {Livingston, Scotland}
    {Oct. 2011 - Jul. 2015}
    {
      \begin{cvitems}
        \item {Responsible for maintaining a database which correlates information concerning the company's energy saving strategy.}
        \item {Retrieve information regarding the store's energy saving performance and update the database accordingly.}
      \end{cvitems}
    }
\end{cventries}
