\cvsection{Technology Summary}
\begin{cventries}
  \cventry
    {Core Skills}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item {\textbf{Languages/Programming}: Java, Python, HTML, CSS, JavaScript, PHP, XML, VBA}
        \item {\textbf{Databases}: MySQL, PostgreSQL, MongoDB, Neo4j, Apache Cassandra}
        \item {\textbf{Software packages}: Microsoft Excel, Documents, Powerpoint. LibreOffice Writer, Calc, Impress.}
        \item {JavaScript}
        \vspace{1mm}
        \begin{itemize}
        \item {Constructed a variety of data visualisations such as choropleth maps, tree maps and waterfall charts using D3 and the Google visualisation API.}
        \end{itemize}
        \item {MySQL and PostgreSQL}
        \vspace{1mm}
        \begin{itemize}
        \item {Created and maintained several MySQL databases including designing a database structure as a relational
        data model for a tour guide company.}                             \vspace{.5mm}
        \item {Implemented and maintained the backend database using PostgreSQL for a wealth management application for financial advisers to control their clients stocks and shares.}
        \end{itemize}
        \item {MS Excel, VBA and Powerpoint}
        \vspace{1mm}
        \begin{itemize}
        \item {Regular use of advanced Excel functionality such as using pivot tables, indirect, index and vlookup.}                          \vspace{.5mm}
        \item {Designed and created multiple VBA scripts to transform client given data into a specified format, easing the overhead 
              for the client and thus securing more internal company revenue.}                            \vspace{.5mm}
        \item {Produced regular slide decks using MS Powerpoint for clients analysing their TV media buy performance.}
        \end{itemize}
        \end{cvitems}
    }
\end{cventries}